Learning to Synthesize Rules for Network Intrusion Detectors

### 2020-02-25 paper/paper.tex
pass on 5.1.2

\newcommand{\textRQtwo}{What is the importance of heuristic functions
  on \tname's performance?}
\vspace{0.2cm}
\begin{itemize}[leftmargin=*,label={}]
\item{\textbf{RQ2.}} \textRQtwo\
\end{itemize}

@@

\newcommand{\textRQthree}{What is the importance of the benign and
  malicious traffic on \tname's performance?}
\vspace{0.2cm}
\begin{itemize}[leftmargin=*,label={}]
\item{\textbf{RQ3.}} \textRQthree\
\end{itemize}

@@

%% On each execution, we captured
%% the incoming traffic to the web server with
%% Wireshark~\cite{wireshark-net-monitor} and used the corresponding pcap
%% files as an input to

%% \tname.\Mar{@Lucas, eu traduzi o que vc. falou
%%   para ingles. Mas, aparentemente, isto esta **inconsistente** com o
%%   que eh dito na Secao~\ref{attack-reproduction}. Por favor,
%%   esclareca!}  \Luc{Essa descrição é referente aos ataques HTTP/TCP da
%%   tabela. O hping3 gera apenas o trafego do SYN Flood. Ambas as
%%   explicações estão corretas. Creio q a descrição da seção 5.2.1 tenha
%%   q ser movida para cá pois está explicando como capturamos o trafego
%%   malicioso. Nós executamos o Nikto e o hping3 uma unica vez para
%%   capturar com o wireshark o trafego q eles geram. O trafego produzido
%%   pelo Nikto ja inclui todos os ataques que utilizamos, nós separamos
%%   os pacotes de cada um deles manualmente utilizando o
%%   wireshark.}\Mar{Fiquei na duvida se o hping soh serve para o SYN
%%   Flood e se/porque o Nikto nao eh usado neste caso...Enfim, nao
%%   precisa responder por aqui. Mova o texto deixando-o *consistente*.}
%%   \tname{} requires the attack to
%% be replayed in order to check whether or not the rule it generates
%% captures the attack.  See function $\mathit{isPlausible}$, used in the
%% minimization algorithm from Section~\ref{sec:minimization}. For all
%% attacks listed on Table~\ref{table:attacks}, we found scripts
%available on the web to replay the attacks. For example,

\Mar{--------------------------- estou aqui!}

\subsubsection{Benign traffic.}\tname{} uses public databases storing benign
traffic for all protocols covered by Suricata (see
Figure~\ref{fig:distribution-rules-protocol}). We used two data sets of
benign traffic. The Bigflows.pcap data set is part of the
TcpReplay~\cite{tcpreplay} open source project. This data set includes
real network traffic of a busy private network access point to the
Internet. According to the TcpReplay web site ``This capture is much
larger and has a smaller average packet size than the previous capture
(smallFlows.pcap). It also has many more flows and different
applications.''. In addition to the Bigflows.pcap data set, we also
used data sets of normal traffic made available by Stratosphere
Lab~\cite{stratosphere-normal}.

>>>>

\newcommand{\textRQtwo}{How important are the heuristic functions
  to \tname's performance?}
\vspace{0.2cm}
\begin{itemize}[leftmargin=*,label={}]
\item{\textbf{RQ2.}} \textRQtwo\
\end{itemize}

@@

\newcommand{\textRQthree}{How important are the benign and
  malicious traffic to \tname's performance?}
\vspace{0.2cm}
\begin{itemize}[leftmargin=*,label={}]
\item{\textbf{RQ3.}} \textRQthree\
\end{itemize}

@@

\subsubsection{Benign traffic.}~Security
tools (e.g., perforation testing tools) often use benign traffic to
evaluate false positive rates. Consequently, different public options
exist. We used two popular public sources. The Bigflows.pcap data set
is part of the TcpReplay~\cite{tcpreplay} open source project. This
data set includes real network traffic of a busy private network
access point to the Internet. According to the TcpReplay web site
``This capture is much larger and has a smaller average packet size
than the previous capture (smallFlows.pcap). It also has many more
flows and different applications.''. In addition to the Bigflows.pcap
data set, we also used data sets\Mar{more than one?} made available by
Stratosphere Lab~\cite{stratosphere-normal}\Mar{is there a description
  of the traffic? as the description for Bigflows.pcap?}.
